\chapter{Design \& Implementation}
\label{ch:implementation}

This chapter covers the design of the automatic testing in this project. It then specifies the Apollo installation details and Dreamview Simulation Environment GUI.

Design containing a comprehensive description of the design chosen, how it addresses the problem, and why it is designed the way it is
Implementation containing a comprehensive description of the implementation of your software, including the language(s) and platform chosen, problems encountered, any changes made to the design as a result of the implementation, etc.

\section{Design of Automatic Testing}
Introduce the first and second stages of the test, and accordingly fuzzing and MT steps.

\subsection{Fuzzing}
Describe how the obstacles are randomly generated in the scene and how is the information of obstacles and collisions are monitored and obtained.

\subsection{MR Generation and MT Implementation}
Present the MRs used and how MT is applied to generated follow-up cases. Explain in detail how the source test cases were restored and how follow-up ones are developed based on source ones and the MRs.

\subsection{Test Script Explanation}
Introduce the programming language (Python) used to write the scripts. Give details of related libraries used in the script and how the data is stored in and read from files.

\section{Apollo Installation and Dreamview Simulation Environment}
Introduce the procedures of Apollo installation, building and debug. Describe the GUI and usage of Dreamview. State the supporting OS, platform and related issues encountered.

\subsection{Building Apollo on Ubuntu 18.04}
Explain that Apollo is only supported in Ubuntu OS (Because it need ROS which can only run on Linux). Specify how Apollo is build on Ubuntu 18.04. 

\subsection{Docker Environment}
Introduce the concepts of Docker and how it is used to provide a running environment of Apollo. Give some instructions or problems encountered.

\subsection{Problems Encountered}
Provide details of technical problems encountered in building Apollo, using Dreamview and running test scripts.